---
title: "Lab 8"
author: "Deanna Elliott"
date: "11/16/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
library(janitor)
```

### Read in slo_homes.csv

```{r}

homes <- read_csv(here("root" , "slo_homes.csv")) %>% 
  clean_names()
  
```

### Create a subset with 4 cities

Task: Create a subset that only contains observations where the city is

- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Marie-Orcutt"

```{r}

homes_subset <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))


#Check if it worked
# unique(homes_subset$city)
```

### A little exploration

Task: Create a summary table that has the mean and sd of home prices grouped by city and sale status

```{r, include = FALSE}

homes_subset %>% 
  group_by(city, status) %>% 
  summarize(mean_price = mean(price), sd_price = sd(price))
```

Task: Explore the relationship between sq footage and home price (from homes_subset) in a scatterplot

```{r}

ggplot(data = homes_subset,
       aes(x = sq_ft, y = price)) +
  geom_point(aes(color = city)) +
  geom_smooth(method = "lm")
```

Trend: Linear with positive correlation between variables, which makes sense; generally larger homes cost more.

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Create 2 different permutations of this model

(1) price ~ city, bedrooms, bathrooms, sqft, status (lm1)
(2) price ~ city, sq ft, status (lm2)
(3) price ~ city, status (lm3)

```{r}

lm1 <- lm(data = homes_subset, price ~ city + bedrooms + bathrooms + sq_ft + status)

lm2 <- lm(data = homes_subset, price ~ city + sq_ft + status)

lm3 <- lm(data = homes_subset, price ~ city + bathrooms + status)

summary(lm3)

# If I wanted SLO to be the reference level:
# Use fct_relevel() to specify a new reference level

# new_homes_subset <- homes_subset %>% 
 #  mutate(city = fct_relevel(city, "San Luis Obispo"))

# lm_slo <- lm(price ~ city + sq_ft, data = new_homes_subset)
```

We would expect a home in SMO to sell for $260,861 less than a very similar home in Arroyo Grande.

R2, lm1 = 53.8% of variance in home price is explained by this model 

### Explore correlations between quantitative variables

Task: Make a subset called homes_quant (from homes_subset) that only contains variables from price to sqft

```{r}

homes_quant <- homes_subset %>% 
  select(price:sq_ft)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse")
```

R2, lm2 = 52.7% of variance in home price is explained by this model

### Compare AIC values

```{r}

AIC(lm1) # lower AIC = better
AIC(lm2)
```

### Use modelsummary() to return multiple model outputs

```{r}

modelsummary(list(lm1, lm2, lm3))
```

### Checkout diagnostic plots for lm1

```{r}

plot(lm1)
```

### Use broom::augment() to return predictions for existing observations

```{r}

home_predict <- augment(lm1)

# make a histogram of the residuals from this model (lm1)

ggplot(data = home_predict, aes(x = .resid)) +
  geom_histogram(bins = 15)

```

